How do changes in ex vary between countries?

### 2022-03-02 draft_paper.Rmd

This notebook will compare annual changes in life expectancy at both birth ($e_0$) and at age 65 ($e_{65}$) in the UK and UK nations, with other select European nations, including a 'Synthetic Germany' created from a weighted average of East and West German data for common years. The method for creating this 'Synthetic Germany' is also described in this and linked documents. 
Adding a line to try contribute

@@

>>>>

This notebook will compare annual changes in life expectancy at both birth ($e_0$) and at age 65 ($e_{65}$) from 1980 to 2019 (or the latest available year) in England and Wales, Scotland, France, Italy, Spains and Germany. Germany includes a 'Synthetic Germany' created from a weighted average of East and West German data for common years. The method for creating this 'Synthetic Germany' is covered in the methods section in brief and in Appendix X for more detail.

@@

In order to explore the hypothesis that the recent stallin in life expectancy, most marked in England and Wales, was an expected 'correction' after a decade of unusually fast life expectancy improvements, we have selected the years from 1980 onwards.
